A Mountaintop View Requires Minimal Sorting: \break An Instance Optimal Contour Tree Algorithm

### 2014-10-29 paint-contour-tree.tex
sanity commit

A large class of data, such as satellite terrain maps, physical simulations, combustion data, can
be thought as a function $f: \RR^d \mapsto \RR$. Typically, a finite representation is given
by consider $f$ to be piecewise linear over some mesh (simplicial complex) $\MM$ in $\RR^d$.
\emph{Contour trees} are a specific topological data structure used to represent and visualize
the function $f$.

@@

For convenience, imagine $f$ to be smooth. All points where the gradient of $f$ is zero are \emph{critical point},
exactly where the topology of the contours change. The vertices of the contour tree are exactly the critical points.

>>>>

A large class of data, such as satellite terrain maps, physical simulation output, and combustion data, can
be thought as a function $f: \RR^d \mapsto \RR$. Typically, a finite representation is given
by considering $f$ to be piecewise linear over some mesh (simplicial complex) $\MM$ in $\RR^d$.
\emph{Contour trees} are a specific topological data structure used to represent and visualize
the function $f$.

@@

For convenience, imagine $f$ to be smooth. All points where the gradient of $f$ is zero are \emph{critical point},
exactly where the topology of the contours change. The vertices of the contour tree are exactly these critical points,
representing the important topological events. An edge connects two critical points if
